\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true,urlcolor=black,linkcolor=black,citecolor=black}
\usepackage{subfig}
\renewcommand{\sectionautorefname}{Section}
\usepackage{enumitem}
\usepackage{balance}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{comment}
% \usepackage{subfigure}
% \usepackage{subfig}
\usepackage{threeparttable}
%\usepackage{siunitx}
\usepackage{microtype}
\usepackage{relsize,xspace}
\usepackage{cite}
\usepackage{textcomp}
\usepackage{mdframed}
\usepackage{framed}

%use the following command to DISABLE all to do notes and comments
%\usepackage[disable]{todonotes}
%use the following command to ENABLE all to do notes and comments
% \usepackage[]{todonotes}

% \newcommand{\tom}[1]{\todo[color=blue!40, inline]{\footnotesize{Tom: #1}}}
% \newcommand{\alex}[1]{\todo[color=orange!40, inline]{\footnotesize{Alex: #1}}}
% \newcommand{\john}[1]{\todo[color=green!40, inline]{\footnotesize{John: #1}}}
% \newcommand{\ahmed}[1]{\todo[color=purple!40, inline]{\footnotesize{Ahmed: #1}}}


\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\newcommand{\variants}{\textit{Variants}}
\newcommand{\pullrequestsmlvfv}{\ensuremath{\textit{PullRequest}_\textit{MLV-FV}}\xspace}
\newcommand{\pullrequestsfvmlv}{\ensuremath{\textit{PullRequest}_\textit{FV-MLV}}\xspace}
\newcommand{\pullrequestsfvfv}{\ensuremath{\textit{PullRequest}_\textit{FV-FV}}\xspace}
\newcommand{\StartingCommits}{\ensuremath{\textit{StartingCommits}}\xspace}
\newcommand{\StartingCommitsCdLOC}{\ensuremath{\textit{StartingCommits}_\textit{cdLOC}}\xspace}
\newcommand{\pullrequestscommlvfv}{\ensuremath{\textit{PullRequestsCom}_\textit{MLV-FV}}\xspace}
\newcommand{\pullrequestscomfvmlv}{\ensuremath{\textit{PullRequestsCom}_\textit{FV-MLV}}\xspace}
\newcommand{\DirectPullCom}{\ensuremath{\textit{DirectPullCom}_\textit{MLV-FV}}\xspace}
\newcommand{\VariabilityPercentage}{\ensuremath{\textit{VariabilityPercentage}}\xspace}
\newcommand{\VariabilityPercentageloc}{\ensuremath{\textit{VariabilityPercentage}_\textit{cdLOC}}\xspace}
\newcommand{\UniqueCom}{\ensuremath{\textit{UniqueCom}}\xspace}
\newcommand{\UniqueCdLOC}{\ensuremath{\textit{Unique}_\textit{cdLOC}}\xspace}
\newcommand{\MergedCom}{\ensuremath{\textit{MergedCom}}\xspace}
\newcommand{\MergedCdLOC}{\ensuremath{\textit{MergedCdLOC}}\xspace}

\newcommand{\TotalDevMLV}{\ensuremath{\textit{TotalDevMLV}}\xspace}
\newcommand{\TotalDevFV}{\ensuremath{\textit{TotalDevFV}}\xspace}
\newcommand{\CommonDevs}{\ensuremath{\textit{CommonDevs}}\xspace}
\newcommand{\TotalDevs}{\ensuremath{\textit{TotalDevs}}\xspace}
\newcommand{\Duration}{\ensuremath{\textit{Duration}}\xspace}
\newcommand{\ForkVariantBacklog}{\ensuremath{\textit{ForkVariantBacklog}}\xspace}
\newcommand{\Inactivity}{\ensuremath{\textit{Inactivity}}\xspace}
\newcommand{\Category}{\ensuremath{\textit{Category}}\xspace}
\newcommand{\Description}{\ensuremath{\textit{Description}}\xspace}

\definecolor{Mycolor2}{HTML}{00F9DE}

\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\Figref}[1]{Figure~\ref{#1}} %use if at beginning of sentence
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\lstref}[1]{Listing~\ref{#1}}

\newcommand{\compactlist}{\setlength{\itemsep}{0pt} \setlength{\parskip}{0pt}}
\newcommand\parhead[1]{\vspace{.26mm}\noindent\textbf{{#1}}.}

\colorlet{Mycolor1}{green!10!orange!90!}
\newcommand{\jb}[1]{{\textsf{John}[\smaller\sffamily\color{blue} #1}]}
\newcommand{\tm}[1]{{\textsf{Tom}[\smaller\sffamily\color{red} #1}]}
\newcommand{\ad}[1]{{\textsf{Decan}[\smaller\sffamily\color{Mycolor2} #1}]}
\newcommand{\az}[1]{{\textsf{Ahmed}[\smaller\sffamily\color{orange} #1}]}
\newcommand{\sd}[1]{{\textsf{Serge}[\smaller\sffamily\color{Mycolor1} #1}]}

\newcommand{\gh}{\textsf{GitHub}\xspace}
\newcommand{\gl}{\textsf{GitLab}\xspace}
\newcommand{\bb}{\textsf{BitBucket}\xspace}
\newcommand{\np}{\textsf{npm}\xspace}
\newcommand{\scp}{\textit{SCP}\xspace}
\newcommand{\go}{\textsf{Go}\xspace}
\newcommand{\js}{\textsf{JavaScript}\xspace}

\newcommand{\npm}{{the \np package distribution platform}\xspace}
%\newcommand{\tb}[1]{}
%\newcommand{\sn}[1]{}
%\newcommand{\jb}[1]{}
\newcommand{\note}[1]{{\color{red}[NOTE: #1]}}

\begin{document}

\title{An Empirical Investigation of Forks as Variants in the npm Package Distribution}


\author{\IEEEauthorblockN{John Businge,\IEEEauthorrefmark{1}
		Alexandre Decan,\IEEEauthorrefmark{2}
	Ahmed Zerouali,\IEEEauthorrefmark{3} 
	Tom Mens\IEEEauthorrefmark{2} and
	Serge Demeyer,\IEEEauthorrefmark{1}}
	\IEEEauthorblockA{\IEEEauthorrefmark{1}University of Antwerp, Antwerp, Belgium}
	\IEEEauthorblockA{\IEEEauthorrefmark{2}University of Mons, Mons, Belgium}
	\IEEEauthorblockA{\IEEEauthorrefmark{3} Vrije Universiteit Brussels, Brussels, Belgium}
	}



\maketitle

\begin{abstract}
Software developers often need to create variants to accommodate different customer segments. These variants have a common code base but also comprise  variant-specific code. A common strategy is to clone (or fork) an existing application and then adapt it to the new requirements. This form of reuse has been enhanced with the advent of social-coding platforms such as \gh, and package distribution platforms like \np. \gh offer facilities for forking, pull requests, and cross-project traceability. \np offers facilities for managing package release dependencies and dependents on the distribution platform. Little is known about the maintenance practices of the variants.
We therefore performed an exploratory investigation on the evolution of variants, focusing on their technical aspects. We collected variants from the \js ecosystem, whose sources are hosted on \gh, and whose packages are  released on \npm. We have identified a significant number of variant forks in this ecosystem. Compared to their mainline repositories, we also found variant forks to have a significant number of package releases, package dependencies, dependent packages and dependent projects.
\tom{This last sentence is not very clear to me. Do you mean that variant forks have more of them than mainline repositories? Also, avoid the term "significant" in the abstract in the paper if you do not use it in the context of "statistical significance". Use another word instead in that case.}

%Social coding platforms like \gh and package distribution platforms like \np have substantially improved both code reuse and collaborative development. The two have provided a huge bazaar of software projects and components that can be reused through forking and package dependencies, respectively. \gh comprises a number of software ecosystems that form
\end{abstract}

\begin{IEEEkeywords}
software variants, npm, depandencies, software ecosystems
\end{IEEEkeywords}

\input{introduction}

\input{methodology}

\input{results}

\input{conclusion}


%\balance
% references section

\bibliographystyle{IEEEtran}
\bibliography{biblio}


\end{document}
